### 2018-01-10 master/paper.tex
Add evaluation of TLSF+TECS

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.

>>>>

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
When the VM is activated, a large memory is allocated and the initialization is performed.
After that, the application is running and the VM is termnated.
The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
TLSF+TECS can visualize the behavior of GC and help to verify its operation.
Furthermore, when the VM is terminated, the memory used by VM is not completely released and a little used memory remains.
In this way, it is useful for finding bugs related to memory, which is hard to find.
